Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-01 paper.tex
update

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity. This approach is consider to be a more applicable and adaptive way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition model that utilise the proposed quality model. In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles, which are decoded from an optimised service queue with the consideration of comprehensive quality.

@@

\section{Background}\label{background}

\subsection{Problem Description}\label{problemDes}

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$. Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one service compositions. Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model defined in \ref{qualityModel} for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

@@

Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper. Therefore, these matches will be used to discover web service candidates for service composition with consideration of the threshold $\alpha$ to enhance the accuracy and efficiency in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}

@@

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both addressed both of them at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.

In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$. A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formula \ref{equation1}, when $\lambda$ = 1 (default value as 0).

\begin{equation}
q(s_ {similarity}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

\begin{equation}
q_{cd}(sl{_{i,j}})={=} \frac{|lcs(Out_{s_i},In_{s_j})|}{|In_{s_{x}} \setminus Out_{s{_y}} \stackrel{.}| +|lcs(Out_{s_i},In_{s_j})| }
 \label{equation2}
\end{equation}

\begin{equation}
\label{equation3}
q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), q_{cd}(sl_{i,j}))
\end{equation}

In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. In details, a sequence of fitness functions are used in the binary selection of chromosome, rather than a single objective consisting of both functional and non-functional quality. Apart from that, match types are ignored in their quality evaluation of semantic matching.

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. This approach is different from \cite{da2016particle}. Here we use weighted graphs as particle presentation while considering a comprehensive quality.

\subsection{Semantic matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}. The purpose of semantic matchmaking quality is to find more component services that satisfies the quality of QoS.

The semantic matchmaking is typically achieved by utilising OWL2 and OWL-S. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL from extension of RDF. which specifies semantic information of concepts involved in MECE. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

\subsection{Ontology-based Index Cached Optimisation}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services. The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types. Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.  The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold $\alpha$.

This implementation contributes to less time and constant time for weighted graph building.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=10cm]{matchmaking.pdf}}}
 \caption{Semantic matchmaking.}
 \label{matchmaking}
\end{figure}

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}. Match type is considered to be one factor for the semantic matchmaking quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new} --- a taxonomy-based measurement for ontology matching. In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.

@@

>>>>

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity. This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition model that utilise the proposed quality model. In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles in the searching space, which are decoded from an optimised service queue with the consideration of comprehensive quality.

@@

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both addressed both of them at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.

In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$. A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$.

In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. In details, a sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality. Apart from that, match types are ignored in their quality evaluation of semantic matching.

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as particles in their PSO algorithm considering QoS optimisation. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.

\section{Problem Description}\label{problemDes}

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

@@

Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper. Therefore, these matches will be used to discover web service candidates for service composition in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}

@@

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. Overall, this approach is different from \cite{da2016particle}, as we use weighted graphs as particle presentation while considering a comprehensive quality.

\subsection{Semantic matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.

The semantic matchmaking is typically achieved by utilising OWL2 and OWL-S. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL from extension of RDF. which specifies semantic information of concepts involved in MECE.

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive}.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}. Match types are considered to be one factor for the semantic matchmaking quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, which is a taxonomy-based measurement for ontology matching. This formula \ref{equation1} is used to estimate the similarity between output-related concept and input-related concept for selecting web services. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
\begin{equation}
q(s_ {similarity}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one service compositions. Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$
